Retrofitting Effect Handlers onto OCaml

### 2020-11-13 retro-concurrency.tex
sec2

\if{0}
\begin{enumerate}[label=R\arabic*]
  \item \textbf{Backwards compatibility} A well-behaved OCaml program does not
    break under OCaml extended with effect handlers. OCaml code that does not
    use effect handlers will pay negligible performance cost.
  \item \textbf{Tool compatibility} OCaml with effect handlers produce
    well-formed backtraces, and remains compatible with program analysis tools
    such as debuggers and profilers that inspect the stack using DWARF stack
    unwind tables.
  \item \textbf{Effect handler efficiency} In order to support
    highly-concurrent applications, the program must accommodate millions of
    continuations at the same time. Installing effect handlers, capturing and
    resuming continuations must be fast.
  \item \textbf{Forwards compatibility} While this work does not present an
    effect system, the design must be compatible with a future effect system
    for OCaml. As a cornerstone of modularity, we also want blocking I/O code
    to \emph{transparently} be made asynchronous with the help of effect
    handlers.
\end{enumerate}
\fi

\noindent \textbf{R1: Backwards compatibility.} A well-behaved OCaml program does
not break under OCaml extended with effect handlers. OCaml code that does not
use effect handlers will pay negligible performance cost.

\noindent \textbf{R2: Tool compatibility.} OCaml with effect handlers produce
well-formed backtraces, and remains compatible with program analysis tools such
as debuggers and profilers that inspect the stack using DWARF stack unwind
tables.

\noindent \textbf{R3: Effect handler efficiency.} In order to support
highly-concurrent applications, the program must accommodate millions of
continuations at the same time. Installing effect handlers, capturing and
resuming continuations must be fast.

>>>>

\if{0}
\begin{enumerate}[label=R\arabic*]
  \item \textbf{Backwards compatibility} A well-behaved OCaml program does not
    break under an OCaml extended with effect handlers. OCaml code that does not
    use effect handlers will pay negligible performance cost.
  \item \textbf{Tool compatibility} OCaml with effect handlers produce
    well-formed backtraces, and remains compatible with program analysis tools
    such as debuggers and profilers that inspect the stack using DWARF stack
    unwind tables.
  \item \textbf{Effect handler efficiency} In order to support
    highly-concurrent applications, the program must accommodate millions of
    continuations at the same time. Installing effect handlers, capturing and
    resuming continuations must be fast.
  \item \textbf{Forwards compatibility} While this work does not present an
    effect system, the design must be compatible with a future effect system
    for OCaml. As a cornerstone of modularity, we also want blocking I/O code
    to \emph{transparently} be made asynchronous with the help of effect
    handlers.
\end{enumerate}
\fi

\noindent \textbf{R1: Backwards compatibility.} A well-behaved OCaml program does
not break under an OCaml that is extended with effect handlers. OCaml code that does not
use effect handlers will pay negligible performance and memory cost.

\noindent \textbf{R2: Tool compatibility.} OCaml programs with effect handlers produce
well-formed backtraces and remain compatible with program analysis tools such
as debuggers and profilers that inspect the stack using DWARF unwind
tables.

\noindent \textbf{R3: Effect handler efficiency.} The program must accommodate millions of
continuations at the same time to support
highly-concurrent applications. Installing effect handlers, capturing and
resuming continuations must be fast.
